---
title: "Week 4 Presentation"
author: "Noelia Carrillo"
date: "5 de diciembre de 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(plyr)
library(datasets)
library(dplyr)
library(ggplot2)
```

## Introduction

This presentation is a part of Data Products Course week 4 project.

Project difinition: 

Create a Shiny application and deploy it on Rstudio's servers. Include:

- Some form of input (widget: textbox, radio button, checkbox, ...)
- Some operation on the ui input in sever.R
- Some reactive output displayed as a result of server calculations

Prepare a reproducible pitch presentation about your application.

The webpage is hosted in RPubs.

## Shiny application

The data set used is HairEyeColor from datasets package.

The user has to select hair color from a list of values. 

The data is presented by hair color or total values.


## Slide with R Output

This is the data of HairEyeColor Dataset.

```{r head, echo = TRUE}
data.frame(HairEyeColor)
```

## Slide with R Code 

The following code repoduce the code used in the shinny app in order to generate the plot

```{r data, echo=TRUE}
data_students <- as.data.frame(HairEyeColor)
data_students$Hair <- factor(data_students$Hair)
hair_color <- unique(data_students$Hair)
hair_color <- factor(c("Total", as.character(hair_color)))
data_hair <- data_students

data_hair <- ddply(data_hair, .(Eye, Sex), summarize, total=sum(Freq, na.rm = TRUE))
g <- ggplot(data_hair, aes(x=Eye, y=total, fill=as.factor(Sex))) +
      geom_bar(stat = "identity", position = "dodge") +
      ggtitle("Total Students by Eye Color") +
      xlab("Eye Color") + ylab("Total Students") +
      guides(fill=guide_legend("Sex")) + theme_bw()
```

